Language-Based Low-Level MPC Security: $\metaprot$ to $\minifed$

### 2024-05-12 ppdp24/examples.tex
checkpoint

The GMW protocol uses secret sharing to represent data flowing through
circuits. In the 2-party case, clients 1 and 2 each share their input
secrets, and use those shares to represent inputs to gates. Outputs
are also represented as shares. We refer to the pair of shares
representing any particular value as a \emph{wire value}, and
we represent them via records of the form
$
\ttt{\{c1 = } v_1\ttt{;c2 = } v_2\ttt{\}} 
$
where $v_1$ and $v_2$ are client 1 and 2's shares respectively.

For full details of the GMW protocol the reader is referred to
\cite{evans2018pragmatic}. Our implementation libary is shown in
Figure \ref{fig-gmw}, with type signatures for the library functions
also shown. We present the And gate since it is
an interesting component. The Figure includes the
following top-level functions:
\begin{itemize}
\item \ttt{encodegmw}: This function encodes client 1's and client 2's
  secret bits called $\ttt{s[1,"s1"]}$ and $\ttt{s[1,"s2"]}$ into two
  distinct wire values (pairs of shares).
\item \ttt{andgmw}: This function defines the gate $\ttt{"g"}$, the
  identifier $\ttt{"g"}$ being used to distinguish randomness used
  within.  In our version client 1 builds the output table (using
  \ttt{andtablegmw})and transfers the correct output share to client 2
  using 1-out-of-4 OT ($\ttt{OT4}$), definable using $\ttt{OT}$, as
  per standard GMW protocol.
\item \ttt{decode}: This function decodes and publishes a wire value
  by $\ttt{xor}$ing the shares. Note that this requires both client 1
  and 2 to publicize their shares.
\end{itemize}
\begin{example}
  \label{example-gmw-andcircuit}
The following program uses our GMW library to define
a circuit with a single And gate and input secrets $\ttt{s1}$ and
$\ttt{s2}$ from client's 1 and 2 respectively:
\begin{verbatimtab}
decode(andgmw("gate0",encodegmw("s1"),encodegmw("s2")))
\end{verbatimtab}
\end{example}

\begin{definition}
  For all $\alpha \in \{ \mesg{w}, \flip{w} \}$ define:
  $$\pmf(\macgv{\alpha} = v) \defeq \sum_{\sigma \in A} \pmf(\sigma')$$
  and define:
  $$\condd{\pmf}{X}{\macgv{\alpha} = v}(\sigma) \defeq  \sum_{\sigma' \in A} \condd{\pmf}{X}{\sigma'}(\sigma)$$
  where $A = \{ \store \in \mems(\{ \elab{\alpha}{1},\elab{\alpha}{2} \} ) \mid
      \cod{\store(\elab{\alpha}{1}) + \store(\elab{\alpha}{2})} = v \}$.
\end{definition}

@@

\begin{lemma}
  If $\condsep{\pmf}{X_1}{X_2}{X_3}$ and
  $\condp{\pmf}{X_2}{\detx{X_4}}$ then $\condsep{\pmf}{X_1}{X_4}{X_3}$.
\end{lemma}

\begin{lemma}
  Given:
  $$
  \begin{array}{c}
  (\varnothing,\andgmw(z,\mesg{x},\mesg{y}) \redxs %\\
  (\prog,\mesg{z})
  \end{array}
  $$
  Then:
  $$
  \condsep
      {\progtt(\prog)}
      {\{ \macgv{\mesg{x}},\macgv{\mesg{y}} \}}
      {\{ \macgv{\mesg{z}} \}}
      {\{ \elab{\mesg{x}}{2},\elab{\mesg{y}}{2},\elab{\mesg{z}}{1},\elab{\mesg{z}}{2} \}}
  $$
  $$
  \conddetx{\progtt(\prog)}{\{ \macgv{\mesg{x}},\macgv{\mesg{y}} \}}{\{ \macgv{\mesg{z}} \}}    
  $$
\end{lemma}

>>>>

The GMW protocol is a garbled binary circuit protocol. In this section
we will assume the 2-party version, though it generalizes to $n$
parties\cite{XXX}. GMW uses a common technique in MPC, which is to
represent values $v$ as distributed shares $v_1$ and $v_2$ with
$v = v_1 \fplus v_2$. This trick maintains secrecy of $v$
from both parties, and in GMW it is used to maintain the intermediate
values of internal gate outputs in circuits. In related literature
the notation $\macgv{x}$ is used to represent the ``true''
value of $x$ and $[x]$ is often used to represent the share of
given party.

To capture this convention, which is used in many other protocols, we
introduce a new naming convention for ``global view'' elements
$\macgv{\mesg{w}}$, which denote the summed value of
$\elab{\mesg{w}}{1}$ and $\elab{\mesg{w}}{2}$ in a protocol
run. This concept integrates program distributions in the
usual manner, as the probability of the outcome of summation
of two variables in the distribution.
\begin{definition}
  For all $\mesg{w}$ define:
  $$\pmf(\macgv{\mesg{w}} = v) \defeq \sum_{\sigma \in A} \pmf(\sigma)$$
  and define:
  $$\condd{\pmf}{X}{\macgv{\mesg{w}} = v}(\sigma) \defeq  \sum_{\sigma' \in A} \condd{\pmf}{X}{\sigma'}(\sigma)$$
  where $A = \{ \store \in \mems(\{ \elab{\alpha}{1},\elab{\alpha}{2} \} ) \mid
      \cod{\store(\elab{\mesg{w}}{1}) + \store(\elab{\mesg{w}}{2})} = v \}$.
\end{definition}

For full details of the GMW protocol the reader is referred to
\cite{evans2018pragmatic}. Our implementation libary is shown in
Figure \ref{fig-gmw}, and includes encoding functions, where
input secrets are split into shares, $\eand$ and $\exor$ gate
functions, and a decoding function. Note that $\exor$ requires
no interaction between parties, while $\eand$ necessitates and
1-of-4 oblivious transfer. The gate computation is
done entirely in secrect, and the decoding function
is where the declassification occurs-- both parties reveal
their shares of the final gate output $\macgv{z}$.

For example, the following program uses our GMW library to define
a circuit with a single \eand gate and input secrets $\ttt{s1}$ and
$\ttt{s2}$ from client's 1 and 2 respectively:
\begin{verbatimtab}
         let s1 = encodegmw("s1") in
         let s2 = encodegmw("s2") in
         decodegmw(andgmw("z",s1,s2))
\end{verbatimtab}
By convention we will assume that all gates are assigned unique output
identifiers $\ttt{"z"}$, and that all programs are in the form
of a sequence of let-bindings followed by a call to $\decodegmw$
wrapping a circuit.

\paragraph{Oblivious Transfer} \cnote{Here is where we
  wave hands about OT.}

\subsubsection{Correctness Proof with Verification Tactics}

\begin{lemma}
  Define:
  $$
  \begin{array}{c}
    \prog_{i} \defeq \\
    \eassign{\mesg{x}}{1}{\flip{x}}{1}; \eassign{\mesg{x}}{2}{\flip{x}}{2}; \\
    \eassign{\mesg{y}}{1}{\flip{y}}{1}; \eassign{\mesg{y}}{2}{\flip{y}}{2} 
  \end{array}
  $$
  Given:
  $$
  \begin{array}{c}
  (\prog_i,\andgmw(z,\mesg{x},\mesg{y}) \redxs %\\
  (\prog,\mesg{z})
  \end{array}
  $$
  Then both of the following conditions hold, where $\iov(\prog) = M$:
  $$
  \condsep
      {\progtt(\prog)}
      {\{ \macgv{\mesg{x}},\macgv{\mesg{y}} \}}
      {\{ \macgv{\mesg{z}} \}}
      {M_{\{2\}} \cup \{ \elab{\mesg{z}}{1},\elab{\mesg{z}}{2} \}}
  $$
  $$
  \conddetx{\progtt(\prog)}{\{ \macgv{\mesg{x}},\macgv{\mesg{y}} \}}{\{ \macgv{\mesg{z}} \}}    
  $$
\end{lemma}

@@

\begin{lemma}
  Given:
  \begin{mathpar}
    \condsep{\pmf}{X_1}{X_2}{X_3}

    \condp{\pmf}{X_1}{\detx{X_2}}

    \condp{\pmf}{X_2}{\detx{X_4}}
  \end{mathpar}
    Then $\condsep{\pmf}{X_1}{X_4}{X_3}$.
\end{lemma}

### 2024-05-12 ppdp24/gmw.tex
checkpoint

\begin{fpfig}[t]{2-Party GMW circuit library with And gate.}{fig-gmw}
{\footnotesize
  \begin{verbatimtab}
    encodegmw(in, i1, i2) {
      m[in]@i2 := (s[in] xor r[in])@i2;
      m[in]@i1 := r[in]@2;
      m[in]
    }

@@

    andgmw(g, v1, v2) {
      let r = r[g] in
      let table = andtablegmw(v1,v2,r) in
      m[g]@2 := OT4(v1,v2,table,2,1);
      m[g]@1 := r@1;
      m[g]
    }

    decodegmw(v) {
      p["1"] := v@1; p["2"] := v@2;
      out@1 := (p["1"] + p["2"])@1;
      out@2 := (p["1"] + p["2"])@2
    }
  \end{verbatimtab}
}
\end{fpfig}

>>>>

\begin{fpfig}[t]{2-Party GMW circuit library.}{fig-gmw}
{\footnotesize
  \begin{verbatimtab}
    encodegmw(in, i1, i2) {
      m[in]@i2 := (s[in] xor r[in])@i2;
      m[in]@i1 := r[in]@2;
      m[in]
    }

@@

    andgmw(z, x, y) {
      let r = r[z] in
      let table = andtablegmw(x,y,r) in
      m[z]@2 := OT4(x,y,table,2,1);
      m[z]@1 := r@1;
      m[z]
    }

    xorgmw(z, x, y) { m[z]@1 := (x+y)@1; m[z]@2 := (x+y)@2; m[z] }

    decodegmw(z) {
      p["1"] := z@1; p["2"] := z@2;
      out@1 := (p["1"] xor p["2"])@1;
      out@2 := (p["1"] xor p["2"])@2
    }
  \end{verbatimtab}
}
\end{fpfig}
